\subsection{Vocational}

%------------------------------------------------

\cventry{05/2016--08/2016}{EEG Data Analyst}{\textsc{Daqri}}{Los Angeles, CA}{}{
	\begin{itemize}
		\item Invented 4 ERP-driven applications for Augmented Reality interactions.  Co-invented additional 2 as second author. Currently in preparation for patent app submission.
		\item Constructed labratory-grade real-time EEG recording, streaming, and analysis stack.
		\item Design and implement interface between the OpenBCI NodeJS library and SCCN's LabStreamingLayer to enable multidevice synchronization and BCILAB-driven analytics using the low-cost OpenBCI EEG device.
		\item Research, analyze and interpret sleeping EEG data using Python's SciPy library. 
	\end{itemize}
}

%------------------------------------------------

\cventry{01/2014--05/2015}{Solo Neuroengineer \& House Captain}{\textsc{Self-Employed}}{San Francisco, CA}{}{
	\begin{itemize}
		\item Helped direct the setup and growth of a 25-person intentional community focused in interdisciplinary intellectual interchange in San Francisco.
		\item Resolved or mediated inter-resident conflicts pursuant to overarching community goals.
		\item Worked on myriad neuroengineering projects, including Moodband, a wearable for EEG-based emotional state visualization; ley*, a MFQ-scheduler-inspired to-do system; Respectable, a social-graph analysis tool; and an Abalone AI competition.
		\item Self-taught and took online courses in chaos, complexity theory, and medical neuroscience.
		\item Researched possible BCIs and wearables, especially in the contexts of potential game designs, mental health, biological robots, and behavioral reinforcement.
	\end{itemize}
	}
%------------------------------------------------
\cventry{05/2013--12/2013}{Software Engineer}{\textsc{Palantir Technologies}}{Palo Alto, CA}{}{
	\begin{itemize}
		\item Expanded and maintained graphing web interface in Javascript and backend Java.
		\item Designed, developed, and implemented additional features to core product in Java Swing.
	\end{itemize}
}

%------------------------------------------------

\cventry{05/2008--08/2011}{Database Architect Intern}{\textsc{Baxter Credit Union}}{Vernon Hills, IL}{}{
	\begin{itemize}
		\item Designed, coordinated, and implemented expansions to database processing capability.
		\item Collaborated with non-technical employees throughout the company to clarify the aims of various projects and subsequently implemented projects according to their specifications.
		\item Trained and led team of new interns in T-SQL programming on several database-improvement projects.
	\end{itemize}
}