\subsection{Lab Experience}

%------------------------------------------------
\cventry{08/2017--Present}{Researcher}{\textsc{Dr. Asbeck's Assistive Robotics Lab}}{Blacksburg, VA}{}{
	\begin{itemize}
		\item Modular EMG sleeve: Redesigning project for simpler, more usable design for incorporation into robotic exoskeletons.
	\end{itemize}
}

\cventry{08/2016--08/2017}{Researcher}{\textsc{Dr. Ratnam's Healthcare Engineering Lab}}{Urbana, IL}{}{
	\begin{itemize}
		\item Created \& used recording software in small team to capture elderly subjects in realistic apartment environments despite occlusion.
		\item Created analysis pipeline to estimate realistic biomechanically-valid body motion from noisy Kinects, force sensors, and IMUs.
		\item Collaborated across numerous disciplines and institutions, including Dr. Sosnoff's Fall Prevention Lab and the Jump Trading Medical Simulation Center in Peoria.
	\end{itemize}
}

\cventry{01/2011--05/2013, 05/2015--05/2016}{Research Engineer}{\textsc{Dr. Hummel's Cognitive Modeling Lab}}{Urbana, IL}{}{
	\begin{itemize}
		\item Expanded LISA model of human abstract reasoning to better reason about complex situations and develop doubt in hypothetical situations using analogies.
		\item Designed \& implemented experiment interfaces and structure to best test working theories of relational visual perception, attention, and memory.
		\item Aided Phd. students in coding, data analysis, and interpretation of relevant theories.
	\end{itemize}
}
%------------------------------------------------

\cventry{08/2012--05/2013}{BCI Researcher}{\textsc{Dr. Bretl's Applied Controls Lab}}{Urbana, IL}{}{
	\begin{itemize}
		\item Researched and implemented novel EEG Brain-Computer Interface, the N2PCSpeller.
		\item Recruited and ran subjects to collect data to test and optimize N2PCSpeller.
	\end{itemize}
}

%------------------------------------------------

\cventry{01/2010--05/2012}{Lab Tech/Analyst}{\textsc{Dr. Federmeier's Neurolinguistics Lab}}{Urbana, IL}{}{
	\begin{itemize}
		\item Assisted graduate students both with writing experiment code and with data mining of ERP results despite abundance of noise and artifacts.
		\item Aided in subject preparation and running in EEG experiments for high subject throughput.
		\item Ensured comfortable atmosphere for subjects despite otherwise abnormal circumstances.
		\item Taught new lab assistants and grad students efficient procedures in use of lab equipment.
	\end{itemize}
}