\section{Current Projects}

\cventry{08/2017--Present}{SocialJustice.Engineering: Complicating the Model}{Hani Awni}{}{}{
	Draws and explores interrelationships between engineering culture, societal conflict, power struggles, and STEM-dominating mythologies in search of a more potent engineering practice absent the influence of the heteropatriarchy. Targets engineering audience by challenging unquestioned assumptions, inspecting popular bifurcations, and, generally, complicating models.
}
\cvitem{Status}{Ongoing. Writing underway.}
\cvitem{Link}{\url{socialjustice.engineering}}

\cventry{03/2017--Present}{Open Repository of Social-Justice-Focused Senior Design Project Proposals for CS \& ECE}{Hani Awni}{}{}{
	Repository of example project proposals at the undergraduate senior thesis level tackling issues of social justice. Provides realistic, undeniably-implementable technical proposals addressing problems commonly deemed a-priori a "social problem" by the engineering community. Project proposals are designed to encourage human-centered design, empower budding engineers to tackle classically 'off-limits' problems like online harassment, doxxing, or astroturfing, and demonstrate to the existing engineering community how reasonably addressable these problems are in reality.
}
\cvitem{Status}{Ongoing. Collaborations underway with UIUC ECE and CS departments. Accumulating \& populating additional project proposals will never end.}
\cvitem{Link}{\url{ppr.socialjustice.engineering}}

\cventry{04/2014--Present}{Automated Externalized Executive Function}{Hani Awni}{}{}{
	Circumvents numerous unwanted symptoms of mental illness, including impaired executive functioning due to depression and ADHD, difficulty initiating day, difficulty maintaining social bonds, persistent imposter syndrome, and difficulty forming narratives of personal productivity, in the form of a digital personal assistant allowing hierarchical project definition \& tracking inspired by GTD productivity methodology and mindfullness-DBT. Semiautomatically reduces entire library of tasks consituting projects, in light of current priorities and available time and context, into current task for immediate execution while forcing focus.
}
\cvitem{Status}{Ongoing. Basic project/task tracking implemented, automation underway.}