
\section{Partial Past Projects List}

\cventry{09/2016--05/2017}{Biomechanically-Valid Motion Capture despite Occlusion using Kinects and IMUs}{Hani Awni \& Drew Douglass}{}{}{Complete, approachable system for localizing elderly patients navigating furnished apartments. Designed to capture in tight, confined spaces throughout a motion despite occlusion by combining multiple Kinects. Designed for integration with whole-body inverse dynamics system.}
\cvitem{Status}{Blocked. Visual capture and body parameterization complete. Composite system pending inverse dynamics solver implementation for verification.}


\cventry{01/2017--03/2017}{'Twelve Thousand Years of STEM' Display}{Cheyenne Syring \& Hani Awni}{}{}{
	Challenges eurocentric narratives of science, technology, and engineering that purport science "began in the Age of Enlightenment" by highlighting the multitudes of non-western pre-existing or ongoing scientific and technological developments across many domains of science and engineering. Will take the form of multiple-poster display situated in a highly-visible semi-permanent installation directly outside of the main Engineering Department advising center in UIUC's Engineering Hall.
}
\cvitem{Status}{Hiatus. Project lead overburdened with other priorities.}

\cventry{10/2016--05/2017}{Toward a Feminist Social Network}{Hani Awni \& Online Collaborators}{}{}{
	Helping steer an in-development open-source twitter competitor, known as Mastodon, toward prioritizing tools for facilitating healthy interaction between users by providing code reviews, feature requests, and sparking community dialogue with the dominant devs. Coordinating with like-minded community members in moderation, feature design, and performing causal analysis of how the technology and the dominant social expectations might be tuned or reconcieved around the needs of activists and community organizers.
}
\cvitem{Status}{Paused. Pending W3C's release of the new ActivityPub protocol for substantially more modifiable structure.}

\cventry{01/2016--05/2016}{Analogical Reasoning May Explain Racists Calling Idris Alba ``Too Street''}{Hani Awni, S. Wilner (Advisor), Dr. J. Hummel (PI)}{}{}{
	Demonstrates that pure analogical reasoning, as implemented in LISA, a neural-network model of human abstract relational reasoning, is sufficient to cause disbelief in a hypothetical African-American Bond after exposure to numerous extant James Bond film plots. Second phase demonstrates how even small amounts of minority representation both prevent such disbelief to reexposure and facilitate positive reactions to minority representation along new dimensions of identity.
}
\cvitem{Status}{Hiatus. Deprioritized while translating additional Bond plots into propositional logic.}

\cventry{08/2015 - 12/2015}{Low Cost MicroUAVs: Off-the-Shelf Remote-Control Beetles}{Hani Awni}{}{}{
	Adapts the Maharbiz lab's work with Jade Flowering beetles as RC UAVs to work with off-the-shelf microcontrollers and radios. Uses ATTiny microcontroller and HM11 BLE module to substantially reduce electronics cost to less than $\$0.25$ per beetle by scaling up the beetle to carry the heavier payload. Needs Hercules, Atlas, or Goliath beetles or similar.
}
\cvitem{Status}{Blocked. Electronics/Firmware complete, yet testing delayed pending access to large beetles and lab. Will resume if I ever live in Southeast Asia.}