\section{Research}

\cvitem{Title}{\emph{AccessibilitySLAMNAV: Navigation for All Bodies, Robotic or Human}}
\cvitem{Authors/Year}{Hani Awni, Dr. A. Shew, Dr. A. Asbeck. Underway}
\cvitem{Description}{Adapts open-source software for autonomous robot mapping, localization, and navigation for use as a minimum-cost, DIY-able wearable mapping device \& webserver of accessibility information. Provides point-to-point campus-scale naviagtion under user-specified access constraint profile via a human-usable web interface and a robot-usable ROS service interface. Built on ROS, RTABMAP, and move\_base.}



\cvitem{Title}{\emph{Body Modeling and Inverse Dynamics: A Modeling Toolkit}}
\cvitem{Authors/Year}{Hani Awni, Dr. Rama Ratnam. 2017}
\cvitem{Description}{Presents a Mathematica toolset for constructing a symbolic physics model of any arbitrary rigid body layout. Produces $\mathbf{M}, \mathbf{C}$ of whole-body dynamics and $\mathbf{T}, \mathbf{J}$ of each body segment. Requires only AP Physics-level geometric reasoning to use.}

\cvitem{Title}{\emph{Open-Source Simulink Model of Planar Arm Motion for Real-Time Control.}}
\cvitem{Authors/Year}{Hani Awni, Dr. M. Hernandez. 2016 (Available by Request)}
\cvitem{Description}{Implemented and documented 2 DOF Simulink model for planar arm motion with realistic muscle behavior. Superior to formerly-used OpenSIM models due to differentiable \& discontinuity-free muscle lengths across entire range of motion.}

\cvitem{Title}{\emph{Towards A Brain Computer Interface Based on the N2PC Event Related Potential.}}
\cvitem{Authors/Year}{Hani Awni, J. Norton, S. Umunna, Dr. K. Federmeier, and Dr. T. Bretl. 2013}
\cvitem{Description}{Demonstrates feasibility of an EEG-driven BCI of my own design, based on the heretofore unused N2pc event related potential. Unlike the more common P300Spellers or SSVEP-Spellers, this BCI does not involve a flashing interface, thus improving comfort for extended use. 1st Senior thesis. Presented at IEEE EMBS NER 2013.}