% resume.tex
% vim:set ft=tex spell:

\documentclass[10pt,letterpaper]{article}
\usepackage[letterpaper,margin=0.75in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage{mdwlist}
\usepackage[T1]{fontenc}
\usepackage{textcomp}
\usepackage{tgpagella}
\pagestyle{empty}
\setlength{\tabcolsep}{0em}

% indentsection style, used for sections that aren't already in lists
% that need indentation to the level of all text in the document
\newenvironment{indentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{#1}}%
	\item[]%
}
{\end{list}}

% opposite of above; bump a section back toward the left margin
\newenvironment{unindentsection}[1]%
{\begin{list}{}%
	{\setlength{\leftmargin}{-0.5#1}}%
	\item[]%
}
{\end{list}}

% format two pieces of text, one left aligned and one right aligned
\newcommand{\headerrow}[2]
{\begin{tabular*}{\linewidth}{l@{\extracolsep{\fill}}r}
	#1 &
	#2 \\
	
\end{tabular*}}

% make "C++" look pretty when used in text by touching up the plus signs
\newcommand{\CPP}
{C\nolinebreak[4]\hspace{-.05em}\raisebox{.22ex}{\footnotesize\bf ++}}

% and the actual content starts here
\begin{document}

\begin{center}
{\LARGE \textbf{Hani Awni}}

905 W Main St.\ \ \textbullet
\ \ Urbana, Il, 61801\\
(224) 715-5995\ \ \textbullet
\ \ hani.awni@gmail.com 
\end{center}

\vspace{-0.8em}
\hrule
\vspace{-0.8em}
\subsection*{Education}
\vspace{-0.8em}
%\begin{indentsection}{\parindent}
%\begin{itemize}
%	\parskip=0.1em

%	\item 
	\headerrow
		{\textbf{University of Illinois: Urbana-Champaign}}
		{\textbf{May 2015-May 2017}}
	\\
	\headerrow
		{\emph{Electrical Engineering BS}}
		{\emph{Last 2 Years GPA: 3.77/4.0}}
	\headerrow
		{\textbf{University of Illinois: Urbana-Champaign}}
		{\textbf{May 2013}}
	\\
	\headerrow
		{\emph{Brain-Machine Interfacing Custom BS, Computer Science Department in College of Engineering}}
		{\emph{GPA: 3.2/4.0}}

		\parskip=-0.3em
	\begin{itemize*}
		\item \textbf{Major Description:} Expanded computer science major with deep and wide background in cognitive science, neuroscience, and signal processing. Third ever custom degree awarded by Engineering College. 
		\end{itemize*}
		\parskip=-0.3em
		\textbf{Relevant Coursework:} Control Theory, State Space Control, Embedded Systems, Machine Learning, Neural Network Modeling, Cognitive Psychology, EEG Design, Integrative Neuroscience, Biomedical Imaging, Neuroethology 
	
%\end{indentsection}
%\end{itemize}



\hrule
\vspace{-.5em}
\subsection*{Publications}
\vspace{-0.3em}
\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{description*}
	\item[]
	Hani Awni, J. Norton, S. Umunna, K. Federmeier, and T. Bretl. Towards A Brain Computer Interface Based on the N2PC Event Related Potential. IEEE EMBS NER 2013 in San Diego, CA, 978-1-4673-1969-0/1021-1024.
\end{description*}
\end{indentsection}


\vspace{-0.5em}
\hrule
\vspace{-0.5em}
\subsection*{Experience}
\begin{indentsection}{\parindent}
%\begin{itemize}
%\vspace{-0.1em}
%	\item
	\headerrow
		{\textbf{Self-Employed}}
		{\textbf{San Francisco, CA}}
	\\
	\headerrow
		{\emph{Independent Neuroengineer \& House Captain}}
		{\emph{April 2014 - May 2015}}
\vspace{-2em}
	\begin{itemize*}
		\item Worked on myriad neuroengineering projects, including Moodband, a wearable for EEG-based emotional state visualization; ley*, a MFQ-scheduler-inspired to-do system; Respectable, a social-graph analysis tool; an Abalone AI competition; and NOS, a generalized BCI in collaboration with Randal Koene.
		\item Taking online courses in chaos and complexity theory, medical neuroscience, robotics, and linear algebra.
		\item Researched possible BCIs, especially in the contexts of both potential game designs and mental health.
		\item Helped direct the setup and growth of a 25-person,  intentional community in San Francisco.
		\item Resolved or mediated inter-resident conflicts with an eye toward the overarching goal of the community.
	\end{itemize*}
\vspace{-0.1em}
%	\item
	\headerrow
		{\textbf{Palantir}}
		{\textbf{Palo Alto, CA}}
	\\
	\headerrow
		{\emph{Software Developer}}
		{\emph{June - December 2013}}
\vspace{-2em}
	\begin{itemize*}
		\item Expanded and maintained web interface in Typescript, Coffeescript, and Java.
		\parskip=0.1em
		\item Designed, developed, and implemented additional feature to core product in Java Swing.
	\end{itemize*}

%	\item
	\headerrow
		{\textbf{Dr. Federmeier's Neurolinguistics Lab, Dr. Hummel's Cognitive Modeling Lab}}
		{\textbf{Urbana, IL}}
	\\
	\headerrow
		{\emph{Lab Technician, Analyst, \& Assistant}}
		{\emph{January 2010 -- May 2013}}
	\vspace{-2em}	
	\begin{itemize*}
		\item Designed \& implemented experiment interfaces to best test working theories.
		\parskip=0.175em
		\item Assisted graduate students both with writing experiment code and with data mining of ERP results despite abundance of noise and artifacts.
		\parskip=0.175em
		\item Aided in setup and running of subjects in EEG experiments, enabling high subject throughput.
		\parskip=0.175em
		\item Ensured a comfortable atmosphere for test subjects despite otherwise abnormal circumstances.
		\parskip=0.175em
		\item Taught new research assistants and graduate students efficient procedures in use of lab equipment.
		\parskip=0.175em
		\item Coded data analysis and results interpretation in light of relevant theories.
	\end{itemize*}

%	\item
	\headerrow
		{\textbf{Baxter Credit Union}}
		{\textbf{Vernon Hills, IL}}
	\\
	\headerrow
		{\emph{Database Architect Intern}}
		{\emph{June 2008 -- August 2011}}
		\vspace{-2em}
	\begin{itemize*}
		\item Designed, coordinated, and implemented expansions to database processing capability.
		\parskip=0.175em
		\item Collaborated with non-technical employees throughout the company to clarify the aims of various projects and subsequently implemented projects according to their specifications.
		\parskip=0.175em
		\item Trained and led new interns in T-SQL programming on several database-improvement projects.
	\end{itemize*}

\end{indentsection}

\vspace{-0.8em}
\hrule
\vspace{-0.5em}

\subsection*{Leadership Positions, Group Membership, Special Interests \& Skills}

\begin{indentsection}{\parindent}
\hyphenpenalty=1000
\begin{itemize}
	\parskip=0.175em
	\item
	Founding Chair of SIGNeuro, 2015. Member of ACM, BMES, IEEE, NESA
	\parskip=0.175em
	\item
	Modeling of intelligence and relational reasoning, particularly using neural networks. 
	\parskip=0.175em
	\item Programming Languages: Java, Python, C++, SQL Variants(POSTGRESQL, T-SQL), OCAML	
	\parskip=0.175em
	\item Other: Unity Engine, NetLogo, \LaTeX
\end{itemize}
\end{indentsection}

\end{document}
